CamIO data analysis

### 2020-05-30 R/01-visualizations.Rmd
Update vizs

```{r}
DT::datatable(
  data.wide,
  class = 'cell-border stripe compact',
  filter = 'top',
  options = list(pageLength = 20, autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Filtered data (wide format)'))
)
```

@@

### Violin & Box plots per guidance mode:

```{r}
plot_ly(
    data.long,
    x = ~mode,
    y = ~time,
    color = ~mode,
    type = 'violin',
    points = 'all',
    box = list(visible = T),
    meanline = list(visible = T),
    showlegend = FALSE,
    colors = "Set1"
  ) %>%
  plotly::layout(
    xaxis = list(title = "Subjects"),
    yaxis = list(title = "Time", range = c(0,120)),
    title = glue('Fig {tc<-tc+1}: Violin + Box-Plots per guidance mode')
  )
```

>>>>

```{r}
DT::datatable(
  data.wide,
  class = 'cell-border stripe compact',
  options = list(pageLength = 20, autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Filtered data (wide format)'))
)
```

@@

### Box-Plots per subject & guidance mode:

```{r}
plot_ly(
    data.long,
    x = ~subject:mode,
    y = ~time,
    color = ~subject:mode,
    type = 'box',
    showlegend = FALSE,
    colors = "Set1"
  ) %>%
  plotly::layout(
    xaxis = list(title = "Subjects"),
    yaxis = list(title = "Time", range = c(0,120)),
    title = glue('Fig {tc<-tc+1}: Violin + Box-Plots per guidance mode')
  )
```

### Lineplot of averages between guidance mode :

```{r}
dat <- data.long %>% Rmisc::summarySE(measurevar="time", groupvars=c("mode", "subject")) %>% print
#dat2 <- data.long %>% mutate(se = se(time))
pd <- position_dodge(0.15)

fig <- dat %>%
  ggplot(aes(x = mode, y = time, color = subject)) + #group=1
  geom_line(position = pd) +
  geom_errorbar(aes(ymin = time - se, ymax = time + se), width = .1, position = pd) +
  geom_point(shape=21, size=2, fill="white", position = pd)

### 2020-05-30 R/Index.Rmd
Update vizs

pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast")

>>>>

pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc")
